Concurrent Programming with CXL

### 2020-06-14 book/paper.tex
Adding appendices

\chapter{Complete List of CXL Values}

@@

\chapter{Complete List of CXL Operators}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & any two CXL values \\
\hline
\texttt{e != e} & any two CXL values \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\end{tabular}
\vspace{1em}

@@

@@

>>>>

\chapter{List of CXL Values}

@@

\chapter{List of CXL Operators}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & any two CXL values \\
\hline
\texttt{e != e} & any two CXL values \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{e if e else e} & middle \texttt{e} must be a Boolean \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{\&(lv)} & \texttt{lv} is an lvalue \\
\hline
\texttt{stop lv} & \texttt{lv} is an lvalue \\
\hline
\end{tabular}
\vspace{1em}

@@

An \emph{lvalue} (short for left hand value of an assignment statement)
is something that can be assigned.  This can be a
shared variable, a process variable, or a dereferenced pointer
variable.  It can also be indexed.  Examples include
\texttt{var}, \texttt{var[e]}, and \texttt{\^{}p}.

@@

\chapter{List of CXL Statements}

CXL currently supports the following statements:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{lv = e} & \texttt{lv} is an lvalue and \texttt{e} is an expression; \\
\hline
\texttt{pass} & do nothing; \\
\hline
\texttt{del lv} & delete; \\
\hline
\texttt{call e} & evaluate \texttt{e}; \\
\hline
\texttt{assert b [, x]} & \texttt{b} is a Boolean.  If \texttt{False}, optionally print expression \texttt{e}; \\
\hline
\texttt{const v = e} & \texttt{v} is an identifier, \texttt{e} is a constant expression; \\
\hline
\texttt{def m(v, ...): S} & \texttt{m} and \texttt{v} are identifiers, \texttt{S} a list of statements; \\
\hline
\texttt{let v = e, ...: S} & \texttt{e} is an expression, \texttt{S} a list of statements; \\
\hline
\texttt{if b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements; \\
\hline
\texttt{while b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements; \\
\hline
\texttt{for v in e: S} & \texttt{e} is a set evaluated in order,
                            \texttt{S} a list of statements; \\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements; \\
\hline
\texttt{spawn p e [, t]} & \texttt{p} is a method, \texttt{e} is an expression, \texttt{t} is an optional tag (an expression) \\
\hline
\texttt{go c e} & \texttt{c} is a context, \texttt{e} is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module. \\
\hline
\end{tabular}
\vspace{1em}

To iterate through a dictionary, list, or tuple, use:
\texttt{for v in keys(e):~S}.

\chapter{List of Modules}

The \texttt{bag} module has various useful methods that operate on bags or
multisets:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{bagEmpty()} & returns an empty bag; \\
\hline
\texttt{bagFromset(s)} & create a bag from set \texttt{s}; \\
\hline
\texttt{bagCount(b, e} & count how many times \texttt{e} occurs in bag \texttt{b}; \\
\hline
\texttt{bagChoose(b)} & like \texttt{choose(s)}, but applied to a bag; \\
\hline
\texttt{bagAdd(pb, e)} & add one copy of \texttt{e} to bag \texttt{\^{}pb}; \\
\hline
\texttt{bagRemove(pb, e)} & remove one copy of \texttt{e} from bag \texttt{\^{}pb}; \\
\hline
\end{tabular}
\vspace{1em}

The \texttt{list} module has various useful methods that operate on lists
or tuples:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq(t, b, f)} & return a \emph{slice} of list \texttt{t} starting
at index \texttt{b} and ending just before index \texttt{f}; \\
\hline
\texttt{append(t, e)} & append \texttt{e} to list \texttt{t}; \\
\hline
\texttt{head(t)} & return the first element of list \texttt{t}; \\
\hline
\texttt{tail(t)} & return all but the first element of list \texttt{t}; \\
\hline
\texttt{qsort(t)} & sort list \texttt{t} using quicksort; \\
\hline
\texttt{sum(t)} & return the sum of all elements in \texttt{t}; \\
\hline
\texttt{list2bag(t)} & convert list \texttt{t} into a bag. \\
\hline
\end{tabular}
